%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Tianyu Du} % Your name
\address{www.tianyudu.com \\ www.github.com/tianyudu} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+1) 647-886-7951 \\ tianyu.du@mail.utoronto.ca} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Toronto, Ontario, Canada} \hfill {\em Sep. 2017 - Jun. 2020(Expected)} 
\\ Honours Bachelor of Science.
\\ Program: Economics \& Mathematics Specialist.
\\ Courses Taken: Real Analysis, Game Theory, Non-linear Optimization. Time Series Analysis, Econometrics, Microeconomics(Ph.D).
\\ Cumulative GPA: 4.00/4.00, Course Average: 94\%.
\\
\\{\bf Stanford University, California, United States} \hfill {\em Jun. 2019 - Aug. 2019} 
\\ Program: Intensive Study in Data Science
\\ Courses taken: Machine learning(Graduate), Data Mining and Analysis(Graduate), Theory of Probability(Undergraduate).
\\ Cumulative GPA: 4.30/4.30, Course Average: 99\%.
\\
\\{\bf Hangzhou Foreign Language School, Zhejiang, China} \hfill {\em Sep. 2014 - Jun. 2017} 
\\ Examinations: General Certificate of Education A-Level(CIE). Advanced Placement(AP).
\\ Activities: Co-founder of HwHumans Student Platform.


\end{rSection}

\begin{rSection}{Scholarships \& Awards}

{\bf Dean's List Scholar(2018-19)} \hfill {\em Jun. 2019}
\\ {\bf International Experience Award} \hfill{\emph May. 2019}
\\ (from Killam American Fund for International Exchange)
\\ {\bf Dean's List Scholar(2017-18)} \hfill {\em Jan. 2018}
\end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Activities \& Projects}
{\bf Patient Data Analysis on PANSS Dataset} \hfill \emph{Jun.2019 - Aug.2019}
\\ \emph{The Final Project for STATS202 at Stanford University (Final Report Class Top)}
\\Positive and Negative Syndrome Scale (PANSS) scores of schizophrenia patients were used to test treatment effects, clustering patients based on prior-treatment scores. Moreover, SVM, random forests, and boosting machines were developed to flag invalid assessments and forecast patients' future states.
\\
\\{\bf Artificial Neural Networks in Economic Forecasting} \hfill \emph{May. 2018 - Jun. 2019}
\\ \emph{Independent Research}
\\ Evaluating and comparing the relative performances of neural networks and traditional models on time series forecasting.
\\
\\{\bf Independent Reading in Mathematics: Mathematical Economics} \hfill \emph{May. 2019 - Jun. 2019}
\\ \emph{Supervisor: Robert J. McCann}
\\ Reading in microeconomic theories with rigorous mathematical proofs.
\\
\\{\bf CIBC Machine Intelligence Hackaton} \hfill \emph{Sep. 2018}
\\ \emph{Finalist Group (Top 5)}
\\ An auto-encoder-decoder architecture neural network was implemented to catch fraud in medical insurance.
\end{rSection}



\begin{rSection}{Research Interests}
Machine Learning Methods for Econometrics and Casual Inferences.
\\Computational Economics, Game Theory, and Market Design.
\\Machine Learning Methods and their Applications on Time Series Forecasting.
\end{rSection}

\begin{rSection}{Skills}
\textbf{Programmings} Python including TensorFlow, PyTorch, Sci-kit Learn, Numpy, and various data visualization toolkits; R; STATA; Matlab; Mathematica; Bash.
\\\textbf{Development} Server deployment on Amazon Web Services (AWS) and Google Cloud Platform (GCP).
\\\textbf{Data Analysis \& Machine Learning} Solid mathematical and statistical foundations for statistical learning models.
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Work Experience}
%
%\begin{rSubsection}{SJ Contracts, Pune}{June 2016}{Site Engineer}{}
%\item On-site internship under this leading construction company. Learned and implemented various aspects such as quantity estimation, labour management and safety precautions.
%\end{rSubsection}
%
%
%\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Academic Achievements} 
% Runners up in B.G.Shirke Vidyarthi Competition for Innovative Project organized by Pune Construction Engineering Research Foundation in January 2018
%\item Won First Prize in Model Making Competition Organized by Symbiosis Institute of Technology, Pune.
%\end{rSection}
%
%\newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
%\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
%\item Co-Organized “ Nirmitee 2017” - a National Symposium of Civil Department of MIT, Pune
%\item Attended a workshop on Autodesk Revit at IIT Bombay in 2014.
%\item Winner of Inter Departmental Football Competition 2015.
%\item Member of the  Rotaract Club Of Pune Pride from 2014 to 2017.
%\item Worked for a start-up company Named OUST as a Regional Marketing Manager
%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

%\end{rSection}
%
%\begin{rSection}{Personal Traits}
%\item Highly motivated and eager to learn new things.
%\item Strong motivational and leadership skills.
%\item Ability to work as an individual as well as in group.
%\end{rSection}
\end{document}
